MSF_Groupwork-NBA_shotlog

### 2016-10-14 MSFGroupwork-NBAHotHand.Rmd
edit document layout
changed some code for accuracy per player

This area of anlysis focuses on investigation of whether playing at 'home' gives the team advantage comparing to playing 'away'.

@@

@@

# accuracy

@@

#accuracy for every second
for (i in (0:23)){
  acc[i, "accuracy"] <- (sum(df$SHOT_CLOCK >= i & df$SHOT_CLOCK < i+1 & df$SHOT_CLOCK != 99 & df$FGM == 1)/           sum(df$SHOT_CLOCK >= i & df$SHOT_CLOCK < i+1 & df$SHOT_CLOCK != 99))}

@@

for (i in (1:nrow(df.acc.players))){
  df.acc.players[i, "acc.per.sec"] <- sum(df.acc.players$'0'[df.acc.players$seconds.left == df.acc.players$seconds.left[i] & df.acc.players$player_id == df.acc.players$players_id[i]])} ### doesnt work as I would like it

>>>>

This area of analysis focuses on investigation of whether playing at 'home' gives the team advantage comparing to playing 'away'.

@@

The potential effects of tiredness and stress on the accuracy of shots are investigated in this part of the analysis.

@@

# accuracy per period

@@

#accuracy for every second
for (i in (0:23)){
  acc[i, "accuracy"] <- (sum(df$SHOT_CLOCK >= i & df$SHOT_CLOCK < i+1 & df$SHOT_CLOCK != 99 & df$FGM == 1)/sum(df$SHOT_CLOCK >= i & df$SHOT_CLOCK < i+1 & df$SHOT_CLOCK != 99))}

@@

### doesnt work as I would like it:

for (i in (1:nrow(df.acc.players))){
  for (j in (0:23)){
    df.acc.players[i, "acc.per.sec"] <- sum(df.acc.players$'1'[df.acc.players$seconds.left == j])}
}
